---
title: "GSE39582"
output: html_notebook
---

From a clinical and molecular perspective, colon cancer (CC) is a heterogeneous disease but to date no classification based on high-density transcriptome data has been established. The aim of this study was to build up a robust molecular classification of mRNA expression profiles (Affymetrix U133Plus2) of a large series of 443 CC and 19 non-tumoral colorectal mucosas, and to validate it on an independent serie of 123 CC and 906 public dataset. We identified and validated six molecular subtypes in this large cohort as a combination of multiple molecular processes that complement current disease stratification based on clinicopathological variables and molecular markers. The biological relevance of these subtypes was consolidated by significant differences in survival. These insights open new perspectives for improving prognostic models and targeted therapies.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

## R markdown
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
getwd()
```
<!-- ## packages -->
<!-- ```{r packages, echo=TRUE, warning=TRUE, paged.print=TRUE} -->
<!-- install.packages("BiocManager") -->
<!-- install.packages("forcats") -->
<!-- install.packages("stringr") -->
<!-- install.packages("ggplot2") -->
<!-- install.packages("ggrepel") -->
<!-- install.packages("readr") -->
<!-- install.packages("tidyr") -->
<!-- install.packages("survminer") -->
<!-- BiocManager::install("GEOquery") -->
<!-- BiocManager::install("limma") -->
<!-- BiocManager::install("pheatmap") -->
<!-- BiocManager::install("org.Hs.eg.db") -->
<!-- ``` -->

## import data

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
readr::local_edition(1) ##use old version of readr because of the error of GEOquery
library(GEOquery)
my_id<-"GSE39582"
gse<-getGEO(my_id)
```
## check how many platforms used
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
length(gse)
gse<-gse[[1]]
gse

pData(gse) ## print the sample information
fData(gse) ## print the gene annotation
exprs(gse) ## print the expression data
```
## Check the normalisation and scales used

# exprs get the expression levels as a data frame and get the distribution
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
summary(exprs(gse))

exprs(gse) <- log2(exprs(gse))
boxplot(exprs(gse),outline=FALSE)
```
## Inspect the clinical variables
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(dplyr)

sampleInfo <- pData(gse)
sampleInfo

```


## restructure the data
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(dplyr)
s_data <- sampleInfo %>% 
  dplyr::select(geo_accession, contains("characteristics"), characteristics_ch1.2, characteristics_ch1.3, characteristics_ch1.4, characteristics_ch1.9, characteristics_ch1.13, characteristics_ch1.14, characteristics_ch1.22,-characteristics_ch1.5, -characteristics_ch1.6, -characteristics_ch1,-characteristics_ch1.7, -characteristics_ch1.8,-characteristics_ch1.10, -characteristics_ch1.11, -characteristics_ch1.12, -characteristics_ch1.15, -characteristics_ch1.16, -characteristics_ch1.17, -characteristics_ch1.18, -characteristics_ch1.19, -characteristics_ch1.20, -characteristics_ch1.21, -characteristics_ch1.23, -characteristics_ch1.24, -characteristics_ch1.25, -characteristics_ch1.26, -characteristics_ch1.27, -characteristics_ch1.28,-characteristics_ch1.29, -characteristics_ch1.30,-characteristics_ch1.31, -characteristics_ch1.32,)

s_data <- s_data %>% 
  dplyr::rename(sex = characteristics_ch1.2,
                age = characteristics_ch1.3,
                stage = characteristics_ch1.4,
                chemotherapy = characteristics_ch1.9,
                os.status = characteristics_ch1.13,
                os.time = characteristics_ch1.14,
                KRAS = characteristics_ch1.22
)

s_data <- s_data %>% 
  mutate(sex = gsub("Sex: ", "", sex, fixed=TRUE),
         age = as.numeric(gsub("age.at.diagnosis (year): ","", age, fixed=TRUE)),
         stage = as.numeric(gsub("tnm.stage: ","", stage, fixed=TRUE)),
         chemotherapy = gsub("chemotherapy.adjuvant: ","", chemotherapy, fixed=TRUE),
         os.status = gsub("os.event: ","", os.status, fixed=TRUE),
         os.time = gsub("os.delay (months): ","", os.time, fixed=TRUE),
         KRAS = gsub("kras.mutation: ","", KRAS, fixed=TRUE)
  )

write.csv(s_data,"s_data.csv")
```

## Exploring the data

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
###----Exporting the data----
library(readr)
full_output <- cbind(fData(gse),exprs(gse))
write.csv(full_output,"gse_full_output_GSE39582.csv")

```

## data restructure
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
features <- fData(gse)
#View(features)
### Look at the features data frame and decide the names of the columns you want to keep
features <- dplyr::select(features, ID, `Gene Symbol`)
features <- tidyr::separate(features,`Gene Symbol`, into = c("Symbol_1","Symbol_2"), sep=" /// ")

full_output <- cbind(features,exprs(gse))

##calculate the mean value of repeated genes
full_output1 <-full_output[,2:588]
full_output1<-full_output1[,-2]
e_data<-full_output1
expr_mean=aggregate(.~Symbol_1,mean,data=e_data)
e_data<-expr_mean
#write_csv(full_output, path="gse_full_output_GSE39582_selected.csv")
### We can now join this to our expression matrix.
#e_data <- exprs(gse) %>% 
  #data.frame %>% 
  #tibble::rownames_to_column("ID") %>% 
  #left_join(features)

e_data

dim(s_data)
dim(e_data)


#final_output<-merge(s_data, e_data, by="geo_accession")
#write.csv(final_output,"final_output.csv")

##match with ferroptosis driver list
driver<-read.csv("driver.csv",header = T, stringsAsFactors = T)

driver_all<-e_data[e_data$Symbol_1 %in% driver$symbol,]

driver_all <- driver_all %>% tidyr::gather(geo_accession, Expression,-Symbol_1,) %>% 
  tidyr::spread(Symbol_1, Expression)
driver_all

#data_driver<- left_join(s_data, driver_all)
data_driver<-merge(s_data,driver_all, by="geo_accession")
colnames(data_driver)[9] <- 'KRAS'

write.csv(data_driver,"clean_data_GSE39582_driver.csv")

##match with ferroptosis suppressor list
suppressor<-read.csv("suppressor.csv",header = T, stringsAsFactors = T)

suppressor_all<-e_data[e_data$Symbol_1 %in% suppressor$symbol,]

suppressor_all <- suppressor_all %>% tidyr::gather(geo_accession, Expression,-Symbol_1,) %>% 
  tidyr::spread(Symbol_1, Expression)
suppressor_all

#data_suppressor<- left_join(s_data, suppressor_all)
data_suppressor<- merge(s_data, suppressor_all,by="geo_accession")
colnames(data_suppressor)[9] <- 'KRAS'

write.csv(data_suppressor,"clean_data_GSE39582_suppressor.csv")

##match with ferroptosis all list
all<-read.csv("driver and suppressor.csv",header = T, stringsAsFactors = T)

all_all<-e_data[e_data$Symbol_1 %in% all$symbol,]

all_all <- all_all %>% tidyr::gather(geo_accession, Expression,-Symbol_1,) %>% 
  tidyr::spread(Symbol_1, Expression)
all_all



#data_all<- left_join(s_data, all_all)
data_all<- merge(s_data, all_all,by="geo_accession")
colnames(data_all)[9] <- 'KRAS'
write.csv(data_all,"clean_data_GSE39582_all.csv")



### all data

e_data <- e_data %>% tidyr::gather(geo_accession, Expression,-Symbol_1,) %>% 
  tidyr::spread(Symbol_1, Expression)
e_data

#data<- left_join(s_data, e_data)
data<- merge(s_data, e_data,by="geo_accession")
colnames(data)[9] <- 'KRAS'
write.csv(data,"clean_data_GSE39582.csv")
```
## machine learning female
```{r random forest female all, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(randomForestSRC)
library(tidyverse)
library(naniar)
## drop NA in KRAS status
#data %>% replace_with_na(replace = list(data = "N/A")) %>% is.na()
female<-filter(data,sex=="Female")

female<-female %>% replace_with_na_all(~.x == "N/A")## replace N/A to NA
female_clean<-female %>% drop_na(KRAS)
female_clean<-filter(female_clean,stage <="3")#,age>="50"

write.csv(female_clean, "GSE39582_KRAS_without NA female.csv")



##random forest model

data_clean<-read.csv("GSE39582_KRAS_without NA female.csv",header = T, stringsAsFactors = T)

f.obj <- rfsrc(KRAS ~ ., data  = as.data.frame(data_clean[,8:22890]))
f.obj

print(vimp(f.obj)$importance)

# VIMP using brier prediction error
print(vimp(f.obj, perf.type = "brier")$importance)

oo <- subsample(f.obj, verbose = FALSE)
# take a delete-d-jackknife procedure for example
vimpCI <- extract.subsample(oo)$var.jk.sel.Z
vimpCI

write.csv(vimpCI,"vimpCI_female.csv")

sig_female<-filter(vimpCI,signif=="TRUE")



# Confidence Intervals for VIMP
tiff(file="Confidence intervals_female.tiff",
width=20, height=20, units="in", res=600)
plot.subsample(oo1)
dev.off()
# Confidence Intervals for VIMP
plot.subsample(oo)
# take the variable "Month" for example for partial plot
#plot.variable(f.obj, xvar.names = "", partial = TRUE)

##Jackknife

library(randomForestSRC)
f.obj <- rfsrc(ï..name ~ ., data = data)
## very small sample size so need largish subratio
reg.smp.o <- subsample(f.obj, B = 25, bootstrap = TRUE)
## summary of results
print(reg.smp.o)
```

## machine learning male
```{r random forest male all, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(randomForestSRC)
library(tidyverse)
library(naniar)
## drop NA in KRAS status
#data %>% replace_with_na(replace = list(data = "N/A")) %>% is.na()
male<-filter(data,sex=="Male")
male<-male %>% replace_with_na_all(~.x == "N/A")## replace N/A to NA
male_clean<-male %>% drop_na(KRAS)
male_clean<-filter(male_clean,age>="50",stage <="3")

write.csv(male_clean, "GSE39582_KRAS_without NA male.csv")



##random forest model

data_clean<-read.csv("GSE39582_KRAS_without NA male.csv",header = T, stringsAsFactors = T)

f.obj <- rfsrc(KRAS ~ ., data  = as.data.frame(data_clean[,8:22890]))
f.obj

print(vimp(f.obj)$importance)

# VIMP using brier prediction error
print(vimp(f.obj, perf.type = "brier")$importance)

oo <- subsample(f.obj, verbose = FALSE)
# take a delete-d-jackknife procedure for example
vimpCI <- extract.subsample(oo)$var.jk.sel.Z
vimpCI

write.csv(vimpCI,"vimpCI_male.csv")

sig_male<-filter(vimpCI,signif=="TRUE")



# Confidence Intervals for VIMP
tiff(file="Confidence intervals_male.tiff",
width=20, height=20, units="in", res=600)
plot.subsample(oo1)
dev.off()
# Confidence Intervals for VIMP
plot.subsample(oo)
# take the variable "Month" for example for partial plot
plot.variable(f.obj, xvar.names = "cystine", partial = TRUE)

##Jackknife

library(randomForestSRC)
f.obj <- rfsrc(ï..name ~ ., data = data)
## very small sample size so need largish subratio
reg.smp.o <- subsample(f.obj, B = 25, bootstrap = TRUE)
## summary of results
print(reg.smp.o)
```

## driver model female
```{r driver, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(randomForestSRC)
library(tidyverse)
library(naniar)
##filter female group from data_driver
female_driver<-filter(data_driver,sex=="Female")

female_driver<-female_driver %>% replace_with_na_all(~.x == "N/A")## replace N/A to NA

female_driver_clean<-female_driver %>% drop_na(KRAS)
female_driver_clean<-filter(female_driver_clean,age>="50",stage <="3")

write.csv(female_driver_clean, "Female GSE39582_KRAS_without NA driver.csv")

##random forest model

female_driver_clean<-read.csv("Female GSE39582_KRAS_without NA driver.csv",header = T, stringsAsFactors = T)



fdriver.obj <- rfsrc(KRAS ~ ., data = as.data.frame(female_driver_clean))
fdriver.obj


vimp_female_driver<-vimp(fdriver.obj)$importance

# VIMP using brier prediction error
print(vimp(fdriver.obj, perf.type = "brier")$importance)

oo1 <- subsample(fdriver.obj, verbose = FALSE)
# take a delete-d-jackknife procedure for example
vimpCI1 <- extract.subsample(oo1)$var.jk.sel.Z
vimpCI1

write.csv(vimpCI1,"vimpCI_female_driver.csv")

sig_female<-filter(vimpCI1,signif=="TRUE")



# Confidence Intervals for VIMP
tiff(file="Confidence intervals_female_driver.tiff",
width=20, height=20, units="in", res=600)
plot.subsample(oo1)
dev.off()
# take the variable "Month" for example for partial plot
plot.variable(fdriver.obj, xvar.names = "ABCC1", partial = TRUE)

##Jackknife

library(randomForestSRC)
iris.obj <- rfsrc(KRAS ~ ., data = female_driver_clean)
## very small sample size so need largish subratio
reg.smp.o <- subsample(iris.obj, B = 25, subratio = .5)
## summary of results
print(reg.smp.o)


```


## driver model male
```{r male driver model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
##filter female group from data_driver
male_driver<-filter(data_driver,sex=="Male")

male_driver<-male_driver %>% replace_with_na_all(~.x == "N/A")## replace N/A to NA
male_driver_clean<-male_driver %>% drop_na(KRAS)
male_driver_clean<-filter(male_driver_clean,age>="50",stage <="3")

write.csv(male_driver_clean, "male GSE39582_KRAS_without NA driver.csv")

##random forest model

male_driver_clean<-read.csv("male GSE39582_KRAS_without NA driver.csv",header = T, stringsAsFactors = T)


mdriver.obj <- rfsrc(KRAS ~ ., data = as.data.frame(male_driver_clean))
mdriver.obj


vimp_male_driver<-vimp(mdriver.obj)$importance

# VIMP using brier prediction error
print(vimp(mdriver.obj, perf.type = "brier")$importance)

oo2 <- subsample(mdriver.obj, verbose = FALSE)
# take a delete-d-jackknife procedure for example
vimpCI2 <- extract.subsample(oo2)$var.jk.sel.Z
vimpCI2

write.csv(vimpCI2,"vimpCI_male_driver.csv")

sig_male<-filter(vimpCI2,signif=="TRUE")

# Confidence Intervals for VIMP
tiff(file="Confidence intervals_male_driver.tiff",
width=20, height=20, units="in", res=600)
plot.subsample(oo2)
dev.off()
# take the variable "Month" for example for partial plot
#plot.variable(mdriver.obj, xvar.names = "X208788_at", partial = TRUE)

##Jackknife

# library(randomForestSRC)
# iris.obj <- rfsrc(KRAS ~ ., data = male_driver_clean)
# ## very small sample size so need largish subratio
# reg.smp.o <- subsample(iris.obj, B = 25, subratio = .5)
# ## summary of results
# print(reg.smp.o)
```

## Matched with full_output with gene symbol
```{r matched gene ID, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
male_vimp<-read.csv("vimpCI_male_driver.csv",header = T, stringsAsFactors = T)

#delete X in the ID column before matching\

male_vimp <- male_vimp %>% 
  mutate(X = gsub("X", "", X, fixed=TRUE))

##matching with full_output
male_genelist<-full_output[full_output$ID %in% male_vimp$X,]

write.csv(male_genelist,"sig_male_genelist.csv")

##female group
female_vimp<-read.csv("vimpCI_female_driver.csv",header = T, stringsAsFactors = T)

#delete X in the ID column before matching\

female_vimp <- female_vimp %>% 
  mutate(X = gsub("X", "", X, fixed=TRUE))

##matching with full_output
female_genelist<-full_output[full_output$ID %in% female_vimp$X,]

write.csv(female_genelist,"sig_female_genelist.csv")
```

# suppressor

## suppressor model female
```{r suppressor, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(randomForestSRC)
library(tidyverse)
library(naniar)
##filter female group from data_suppressor
female_suppressor<-filter(data_suppressor,sex=="Female")

female_suppressor<-female_suppressor %>% replace_with_na_all(~.x == "N/A")## replace N/A to NA
female_suppressor_clean<-female_suppressor %>% drop_na(KRAS)
female_suppressor_clean<-filter(female_suppressor_clean,age>="50",stage <="3")

write.csv(female_suppressor_clean, "Female GSE39582_KRAS_without NA suppressor.csv")

##random forest model

female_suppressor_clean<-read.csv("Female GSE39582_KRAS_without NA suppressor.csv",header = T, stringsAsFactors = T)

fsuppressor.obj <- rfsrc(KRAS ~ ., data = as.data.frame(female_suppressor_clean))
fsuppressor.obj


vimp_female_suppressor<-vimp(fsuppressor.obj)$importance

# VIMP using brier prediction error
print(vimp(fsuppressor.obj, perf.type = "brier")$importance)

oo3 <- subsample(fsuppressor.obj, verbose = FALSE)
# take a delete-d-jackknife procedure for example
vimpCI3 <- extract.subsample(oo3)$var.jk.sel.Z
vimpCI3

write.csv(vimpCI3,"vimpCI_female_suppressor.csv")

sig_female<-filter(vimpCI3,signif=="TRUE")



# Confidence Intervals for VIMP
tiff(file="Confidence intervals_female_suppressor.tiff",
width=20, height=20, units="in", res=600)
plot.subsample(oo3)
dev.off()

# take the variable "Month" for example for partial plot
#plot.variable(fsuppressor.obj, xvar.names = "X1552873_s_at", partial = TRUE)

##Jackknife

# library(randomForestSRC)
# iris.obj <- rfsrc(KRAS ~ ., data = female_suppressor_clean)
# ## very small sample size so need largish subratio
# reg.smp.o <- subsample(iris.obj, B = 25, subratio = .5)
# ## summary of results
# print(reg.smp.o)


```


## suppressor model male
```{r male suppressor model, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
##filter female group from data_suppressor
male_suppressor<-filter(data_suppressor,sex=="Male")

male_suppressor<-male_suppressor %>% replace_with_na_all(~.x == "N/A")## replace N/A to NA
male_suppressor_clean<-male_suppressor %>% drop_na(KRAS)
male_suppressor_clean<-filter(male_suppressor_clean,age>="50",stage <="3")

write.csv(male_suppressor_clean, "male GSE39582_KRAS_without NA suppressor.csv")

##random forest model

male_suppressor_clean<-read.csv("male GSE39582_KRAS_without NA suppressor.csv",header = T, stringsAsFactors = T)


msuppressor.obj <- rfsrc(KRAS ~ ., data = as.data.frame(male_suppressor_clean))
msuppressor.obj


vimp_male_suppressor<-vimp(msuppressor.obj)$importance

# VIMP using brier prediction error
print(vimp(msuppressor.obj, perf.type = "brier")$importance)

oo4 <- subsample(msuppressor.obj, verbose = FALSE)
# take a delete-d-jackknife procedure for example
vimpCI4 <- extract.subsample(oo4)$var.jk.sel.Z
vimpCI4

write.csv(vimpCI4,"vimpCI_male_suppressor.csv")

sig_male<-filter(vimpCI4,signif=="TRUE")

# Confidence Intervals for VIMP
tiff(file="Confidence intervals_male_suppressor.tiff",
width=20, height=20, units="in", res=600)
plot.subsample(oo4)
dev.off()
# take the variable "Month" for example for partial plot
#plot.variable(msuppressor.obj, xvar.names = "X208788_at", partial = TRUE)

##Jackknife

# library(randomForestSRC)
# iris.obj <- rfsrc(KRAS ~ ., data = male_suppressor_clean)
# ## very small sample size so need largish subratio
# reg.smp.o <- subsample(iris.obj, B = 25, subratio = .5)
# ## summary of results
# print(reg.smp.o)
```
## Matched with full_output with gene symbol
```{r matched gene ID, echo=TRUE, message=TRUE, warning=TRUE, paged.print=TRUE}
male_vimp<-read.csv("vimpCI_male_suppressor.csv",header = T, stringsAsFactors = T)

#delete X in the ID column before matching\

male_vimp <- male_vimp %>% 
  mutate(X = gsub("X", "", X, fixed=TRUE))

##matching with full_output
male_genelist<-full_output[full_output$ID %in% male_vimp$X,]

write.csv(male_genelist,"sig_male_genelist_suppressor.csv")

##female group
female_vimp<-read.csv("vimpCI_female_suppressor.csv",header = T, stringsAsFactors = T)

#delete X in the ID column before matching\

female_vimp <- female_vimp %>% 
  mutate(X = gsub("X", "", X, fixed=TRUE))

##matching with full_output
female_genelist<-full_output[full_output$ID %in% female_vimp$X,]

write.csv(female_genelist,"sig_female_genelist_suppressor.csv")
```

# all

## all model female
```{r all, message=TRUE, warning=TRUE, include=FALSE}
library(randomForestSRC)
library(tidyverse)
library(naniar)
##filter female group from data_all
female_all<-filter(data_all,sex=="Female",stage <="3")#age>="50"

female_all<-female_all %>% replace_with_na_all(~.x == "N/A")## replace N/A to NA
female_all_clean<-female_all %>% drop_na(KRAS)

write.csv(female_all_clean, "Female GSE39582_KRAS_without NA all.csv")

##random forest model

female_all_clean<-read.csv("Female GSE39582_KRAS_without NA all_clean_0803.csv",header = T, stringsAsFactors = T)

fall.obj <- rfsrc(KRAS ~ ., data = as.data.frame(female_all_clean))
fall.obj


vimp_female_all<-vimp(fall.obj)$importance

# VIMP using brier prediction error
print(vimp(fall.obj, perf.type = "brier")$importance)

oo5 <- subsample(fall.obj, verbose = FALSE)
# take a delete-d-jackknife procedure for example
vimpCI5 <- extract.subsample(oo5)$var.jk.sel.Z
vimpCI5

write.csv(vimpCI5,"vimpCI_female_all.csv")

sig_female<-filter(vimpCI5,signif=="TRUE")



# Confidence Intervals for VIMP
tiff(file="Confidence intervals_female_all.tiff",
width=20, height=20, units="in", res=600)
plot.subsample(oo5)
dev.off()

# take the variable "Month" for example for partial plot
#plot.variable(fall.obj, xvar.names = "X1552873_s_at", partial = TRUE)

##Jackknife

# library(randomForestSRC)
# iris.obj <- rfsrc(KRAS ~ ., data = female_all_clean)
# ## very small sample size so need largish subratio
# reg.smp.o <- subsample(iris.obj, B = 25, subratio = .5)
# ## summary of results
# print(reg.smp.o)


```


## all model male
```{r male all model, echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE}
##filter female group from data_all
male_all<-filter(data_all,sex=="Male",stage<="3")#age>="50"

male_all<-male_all %>% replace_with_na_all(~.x == "N/A")## replace N/A to NA
male_all_clean<-male_all %>% drop_na(KRAS)

write.csv(male_all_clean, "male GSE39582_KRAS_without NA all.csv")

##random forest model

male_all_clean<-read.csv("male GSE39582_KRAS_without NA all_clean_0803.csv",header = T, stringsAsFactors = T)


mall.obj <- rfsrc(KRAS ~ ., data = as.data.frame(male_all_clean))
mall.obj


vimp_male_all<-vimp(mall.obj)$importance

# VIMP using brier prediction error
print(vimp(mall.obj, perf.type = "brier")$importance)

oo6 <- subsample(mall.obj, verbose = FALSE)
# take a delete-d-jackknife procedure for example
vimpCI6 <- extract.subsample(oo6)$var.jk.sel.Z
vimpCI6

write.csv(vimpCI6,"vimpCI_male_all.csv")

sig_male<-filter(vimpCI6,signif=="TRUE")

# Confidence Intervals for VIMP
tiff(file="Confidence intervals_male_all.tiff",
width=20, height=20, units="in", res=600)
plot.subsample(oo6)
dev.off()
# take the variable "Month" for example for partial plot
#plot.variable(mall.obj, xvar.names = "X208788_at", partial = TRUE)

##Jackknife

# library(randomForestSRC)
# iris.obj <- rfsrc(KRAS ~ ., data = male_all_clean)
# ## very small sample size so need largish subratio
# reg.smp.o <- subsample(iris.obj, B = 25, subratio = .5)
# ## summary of results
# print(reg.smp.o)
# ```
## Matched with full_output with gene symbol
```

## matched all
```{r matched al, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
male_vimp<-read.csv("vimpCI_male_all.csv",header = T, stringsAsFactors = T)

#delete X in the ID column before matching\

male_vimp <- male_vimp %>% 
  mutate(X = gsub("X", "", X, fixed=TRUE))

##matching with full_output
male_genelist<-full_output[full_output$ID %in% male_vimp$X,]

write.csv(male_genelist,"sig_male_genelist_all.csv")

##female group
female_vimp<-read.csv("vimpCI_female_all.csv",header = T, stringsAsFactors = T)

#delete X in the ID column before matching\

female_vimp <- female_vimp %>% 
  mutate(X = gsub("X", "", X, fixed=TRUE))

##matching with full_output
female_genelist<-full_output[full_output$ID %in% female_vimp$X,]

write.csv(female_genelist,"sig_female_genelist_all.csv")
```



# Survival
```{r female survival, echo=TRUE, message=TRUE, warning=TRUE, paged.print=TRUE}
male_all<-filter(data_all,sex=="Male",age>="55",stage<="3")

data<-data %>% replace_with_na_all(~.x == "N/A")## replace N/A to NA
data_clean<-data %>% drop_na(KRAS)

write.csv(data_clean, "GSE39582_KRAS_without NA.csv")

library(randomForestSRC)
data(peakVO2, package = "randomForestSRC")
dta <- peakVO2
obj <- rfsrc(Surv(ttodead,died)~., dta,
             ntree = 1000, nodesize = 5, nsplit = 50, importance = TRUE)
print(obj)

```

